{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
remove incorrect 'a'
corrected typo

Now we come to the semantics part. The main idea is to build a the semantics
for multithreaded programs by combining the semantics for sequential programs
with a scheduler.

All active\footnote{A thread is active from \texttt{start \textit{pc}} until
it reaches the \texttt{exit} point.} threads are collected in a set $Thead$.
The state of the concurrent running threads ($ConcState$) is defined as the
product of the partial function space $(Thread \rightharpoonup LocState)$
and the set of global memories $GMemory$. Where $LocState$ is the internal
memory of a thread, from there no information can leak and the $GMemory$ is
the critical part of the system, because it is a memory shared between all
active threads.

>>>>

Now we come to the semantics part. The main idea is to build the semantics
for multithreaded programs by combining the semantics for sequential programs
with a scheduler.

All active\footnote{A thread is active from \texttt{start \textit{pc}} until
it reaches the \texttt{exit} point.} threads are collected in a set $Thread$.
The state of the concurrent running threads ($ConcState$) is defined as the
product of the partial function space $(Thread \rightharpoonup LocState)$
and the set of global memories $GMemory$. Where $LocState$ is the internal
memory of a thread, from there no information can leak and the $GMemory$ is
the critical part of the system, because it is a memory shared between all
active threads.
